Sperm should evolve to make female meiosis fair.

### 2014-05-17 writeup_and_notes/male_dependent_drive.tex
yb read text through the end of the results

\section*{Introduction}
Despite the apparent unity of the organism, `selfish' alleles can
gain an evolutionary advantage at a cost to  individual fitness
\citep{Burt2006}, often by exploiting meiosis and gametogenesis.
Because only one of the four products of female meiosis is transmitted to the egg, female meiosis is particularly vulnerable to such exploitation \citep{Sandler1957,Pardo-ManuelDeVillena2001a}. 
An allele that biases female meiosis in its favor (i.e. a meiotic driver), may increase in frequency even if it entails a pleiotropic fitness cost \citep{Prout1973}, generating a genetic conflict between the success of the driver and organismal fitness.
Meiotic drivers observed in both plants
\citep{Buckler1999,Fishman2005,Fishman2008}, and animals
\citep{Agulnik1990,Wu2005,Pardo-ManuelDeVillena2001c} highlight this
conflict -- the selfish benefits and the associated
pleiotropic fitness costs of drive sustain a balanced polymorphism
\citep{Prout1973}, 
and often generate ongoing evolutionary escalations of drive suppressors and enhancers \citep{Dawe1996,Fishman2008}. 
The threat of meiotic drive to organismal fitness is potentially so
severe that many basic properties of
meiosis and o\"{o}genesis, including the initial genome doubling in
meiosis I \citep{Haig1991}, arrested female meiosis
\citep{Mira1998}, the structure of centromere machinery \citep{Malik2002a,Malik2009,Malik2009}, and sex differences in the recombination rate \citep{Haig2010,Brandvain2012} 
have perhaps evolved to enforce fairness by disrupting meiotic drive \citep{Rice2013}.

@@

In the standard single-locus, biallelic model of female meiotic drive,
the driving allele is transmitted to the egg in heterozygotes with
probability  $d > 1/2$, regardless of sperm genotype (Model 1) \gc{REF}. The timing of fertilization relative to female meiosis places another constraint on $d$, for example, if fertilization (and therefore, sperm dependent drive) takes place at MII (as in mammals),
	female drive requires an uneven number of crossovers between the centromere and the drive locus, 
	so $d$ is bounded to be $<0.83$ \citep[see ][ for
        discussion]{Buckler1999}.  To depict a case
of a self-promoting meiotic driver,  we modify this standard model such 
	that the driver is only effective when fertilized by a sperm carrying that allele (see Figure \ref{Eggsperm_2_allele_cartoon} and Model 2 in the Supplementary Worksheet)
We then identify the conditions allowing for the spread of this self-promoting driver, 
	and evaluate whether a driver of this form could generate a sustained conflict favoring the evolution of suppressors. 
We concluded with an analysis of a related model (Model 3) - in which
drivers influence their transmission in females via paternal genotype,
rather than sperm haplotype.

@@

When a self-promoting driver does spread, 
	it spends much time at low frequency, 
	because the paucity of complimentary sperm compromises its ability to drive. 
However, once relatively common, it  rapidly achieves fixation due to its
	positive frequency dependent behavior (Inset in Figure \ref{Invasion_space}).  
%This lack of a balanced polymorphism %(Figure \ref{Invasion_space}) 
%	precludes the evolution of an
%	allele that suppresses this form of meiotic drive in females.
The positive frequency dependence of a self-promoting driver can also
	induce bistability in its spread -- some values of $s$ 
	allow the fixation of this driver when common, but 
	preclude its invasion when rare (Equation \ref{ineqA}). 
In this case, the driver will be fixed if it reaches a frequency greater than some threshold, 
	approximated in Equation \ref{bistab_homozy_approx} and  presented exactly in 
	Figure \ref{Bistab_homozyg_cost_fig}, and lost otherwise. 
For most parameters, this threshold is likely too high to be reached by drift, 
	and therefore  the fate of self-promoting drivers is determined
	by the more restrictive invasion criteria rather than the fixation criteria.

@@

%OLD YANIV WORDS
% Compared to the invasion criteria, the parameter space
% allowing the fixation of the allele if it is above a cutoff frequency is much broader -- 
% 	a common, recessive, self-promoting driver fixes if
%         $s<(2d-1)/2$ approximately. 
% Therefore, when $(2 d - 1)/(4 d)<s<(2d-1)/(2)$, 
% 	a recessive, self-promoting driver will deterministically fix if drift, mutation, 
% 	or migration pressure bring its frequency above $(1-2d+4ds)/(2s(2d-1))$, 
% 	but it will be lost otherwise.
Inclusion of a heterozygous fitness cost (i.e. $w_{AB}=1-s_h$)
	further constrains the evolution of a self-promoting driver. 
In fact, with any heterozygous fitness cost, a rare self-promoting
	driver is always selected against. 
However, this case also displays bistability -- 
	when $s$ is sufficiently small (Equation \ref{sForHetFix}) this allele fixes deterministically if its 
	frequency exceeds some threshold,  (Equation \ref{thresh2}, exact results in 
	Figure \ref{bistable_additive}).
%	$f_B^*$
%	because it pays the  heterozygous fitness cost but drives
 %      ineffectively (see Figure S\ref{bistable_additive})
%While a standard female driver invades from low frequency when the transmission advantage outweighs the fitness cost (XXX),
%	a rare self-promoter pays a fitness cost, but drives only weakly because complementary sperm are uncommon. 
%This frequency-independent fitness cost, and positive frequency dependent drive generates a bistable system. 
%Below a cutoff frequency the self-promoter driver deterministically decreases in frequency 
%	because it pays the  heterozygous fitness cost but drives
 %      ineffectively (see Figure S\ref{bistable_additive}). 
%Above this frequency, the allele increases deterministically because the commonness of complementary sperm 
%	make drive effective enough to overcome the associated fitness cost.
This bistability prevents self-promoting drivers from invading 	
	reasonably sized populations, and assures that if they do invade, they will rapidly fix.
Our model therefore predicts that self-promoting drivers will not be
	observed as stable polymorphisms in natural populations. 
This lack of a balanced polymorphism %(Figure \ref{Invasion_space}) 
	precludes the evolution of an
	allele that suppresses this form of meiotic drive in females.

Although the allelic identity of sperm could plausibly influence the outcome of female meiosis, 
	limited gene expression in sperm \citep[e.g.][]{Joseph2004}
	suggest a model where sperm influence female meiosis via expression of the fertilizing male's
	diploid genotype (perhaps due to proteins and RNAs packaged into the sperm), rather than sperm haplotype.
This paternal-genotype dependent model (Model 3) requires one additional parameter, as we exchange $d$ in the sperm dependent case for $d_{het}$ and $d_{hom}$ which describe the transmission of the drive allele in a heterozygous female mating with males heterozygous and homozygous for the self-promoting drive allele, respectively.  
Here, a rare driver invades when $s$ is less than $(d_{het}-1/2)/d_{het}$, and usually fixes when it invades.
	% fixes when $s$ is less than $d_{hom} - 1/2$.
However, when the distorting effect of genotype displays strong dominance in its
	effect on female meiosis ($d_{het}$ is close to $d_{hom}$), 
	there is a a narrow sliver of parameter space sustains a polymorphism
	when the cost of the drive is recessive
	(see Figure \ref{Effect_of_dominance}, and Equation \ref{polymale}).  
%Presumably this zone of polymorphism comes about because positive frequency 
%	dependence diminishes with the dominance of the male effect driver. 
%As an analytical example, consider the case of male-genotype dependent deleterious recessive female driver (assuming, as above, $w_{BB}=1-s$, and $w_{AA}=w_{AB}=1$). 
%Here, a rare driver invades when $s$ is less than $(d_{het}-1/2)/d_{het}$, and fixes when $s$ is less than $d_{hom} - 1/2$.
%Intermediate values of $s$, which represent a small proportion of parameter space can maintain a polymorphism. 
While mathematically interesting, it does not seem particularly realistic to think that the
	effect of the drive allele would be dominant in its action through the
	male genotype, while the cost would be recessive. 
Therefore, although Model 3 can sustain a polymorphism, 
	the lack of biological reality underlying the small portion of parameter values 
	required for this polymorphism make us doubt it general applicability. 
%Thus we regard this case as interesting but not very general.

@@

Models 2 and 3, above, explored the dynamics of an allele drove in females when signaled by a complementary signal in sperm.   
We complement this single-locus approach %of an allele with pleiotropic effects in both sexes, 
	with alternative models of two linked loci - one a female driver, 
	and the other, a sperm allele which modifies the effect of drive upon fertilization. 
In this model, a female meiotic driver with no sperm-dependency 
	initially reaches drive-viability equilibrium (with two alleles
	$A$ and $B$ are the ancestral non-driver and driver alleles). 
Subsequently, a sperm-acting modifier of female meiotic drive arises tightly
        linked to this balanced locus (effectively creating a third
        allele/haplotype at this locus). 
Tight linkage offers the best
        chance for a collaboration to evolve between a driver and
       an enhancer of the drive, as recombination breaks up drive haplotypes \citep{Thomson1974,Charlesworth1978,Haig1991}. 
Additionally, tight linkage between female driver and sperm modifier is consistent with the nature of well characterized drive systems which are often maintained as polymorphic inversions with numerous linked modifiers \gc{CITE}.

@@

%%%sperm-acting facilitator
We first consider a sperm-acting modifier of
	female meiotic drive tightly linked to the $B$ background (Model 4).
We treat this non-recombining drive/modifier haplotype as a third allele, and we label this allele as $B^+$ when it enhances drive. 
%(i.e. the non-recombining haplotype of a
 %       driver allele and sperm-acting drive modifier)
%The $B^+$ allele 
%	the $B$ and  $B^{+}$ drive in $AB$ and $AB^{+}$ heterozygotes (see Figure \ref{Eggsperm_3_allele_cartoon})
%		generating a third `$B^{+}$' allele (i.e. the non-recombining haplotype of a
   %     driver allele and sperm-acting drive modifier). 
The $B^+$ allele acts in sperm to increase the effectiveness of drive for both
	the $B$ and  $B^{+}$ alleles in $AB$ and $AB^{+}$ heterozygotes (see Figure \ref{Eggsperm_3_allele_cartoon}). 
%	for a simple schematic of this drive model.  
Naively, $B^{+}$ may spread by capitalizing on the additional drive it causes; however,  
	this is not the case for a few simple reasons. 
First, %the sperm-acting drive facilitator (
	the novel $B^{+}$ haplotype
	%) 
	arises when the ancestral driver 
	%($B$) 
	is at drive-selection balance, 
	and therefore immediately suffers a homozygous fitness cost.  
Worse yet, a novel $B^{+}$ haplotype most often helps 
	the $B$  allele drive ($B^+$ sperm meeting $AB$ eggs), because $B$ is initially more common than $B^{+}$. 
%As $B^{+}$ facilitates $B$ these interactions frequently form 
%	$BB^{+}$ heterozygotes that suffer the same fitness costs as $BB$. 
Therefore, a sperm-acting drive facilitator alleles experience a profound disadvantage 
	in this scenario, even more so than under the previous two allele model. 
We have found no parameter range of this
	three allele system that allows the sperm-acting drive facilitator $B^{+}$ to
	invade the population (eqn. \eqref{coupling}, Appendix Model 4, Mathematical Supplement).

%%%sperm-acting drive suppressors
While  sperm enhancement of a female drive cannot displace a polymorphic female driver, sperm based drive suppressors can. 
%	that is sperm-acting alleles that act to restore  fairness of female meiosis, can. %If these sperm-acting drive suppressors arise on
If a sperm-acting allele that restores fairness to female meiosis arises on
	the drive background (creating a third allele $B^{-}$, Model 4), it displaces the ancestral driver (Equation \ref{coupling}), 
	and often returns to a lower equilibrium frequency than the the $B$ allele, further decreasing the extent of drive in the population.  
If this sperm-acting drive suppressor arises on 
	the non-driving $A$ background (creating a third allele $A^{-}$, Model 5), 
	or is unlinked to the drive locus (Model 6), it readily invades a population segregating
	for the drive system (Figure \ref{Eggsperm_3_allele_cartoon} and eqns \ref{A-} and \ref{unlinked}).  
This allele lowers the frequency of the original drive system (perhaps to zero),
	and spreads to fixation if it does not carry strong fitness costs
	(Figure \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}A). 
This result is consistent with previous work showing that drive suppressors unlinked to, or in repulsion phase with drivers usually invade polymorphic drive systems \citep[e.g. ][]{Brandvain2012}.  
Therefore, all two-locus models of sperm influence on female drive suggest that
	sperm will evolve to oppose female meiotic drive.

>>>>

\section*{Introduction}
Despite the apparent unity of the organism, `selfish' alleles can
gain an evolutionary advantage at a cost to  individual fitness
\citep{Burt2006}, often by exploiting meiosis and gametogenesis.
Because only one of the four products of female meiosis is transmitted to the egg, female meiosis is particularly vulnerable to such exploitation \citep{Sandler1957,Pardo-ManuelDeVillena2001a}. 
An allele that biases female meiosis in its favor (i.e. a meiotic driver), may increase in frequency even if it entails a pleiotropic fitness cost \citep{Prout1973}, generating a genetic conflict between the success of the driver and organismal fitness.
Meiotic drivers observed in both plants
\citep{Buckler1999,Fishman2005,Fishman2008}, and animals
\citep{Agulnik1990,Wu2005,Pardo-ManuelDeVillena2001c} highlight this
conflict -- the selfish benefits and the associated
pleiotropic fitness costs of drive sustain a balanced polymorphism
\citep{Prout1973}, 
and often generate ongoing evolutionary escalations of drive suppressors and enhancers \citep{Dawe1996,Fishman2008}. 
The threat of meiotic drive to organismal fitness is potentially so
severe that many basic properties of
meiosis and o\"{o}genesis, including the initial genome doubling in
meiosis I \citep{Haig1991}, arrested female meiosis
\citep{Mira1998}, the structure of centromere machinery \citep{Malik2002a,Malik2009}, and sex differences in the recombination rate \citep{Haig2010,Brandvain2012} 
have perhaps evolved to enforce fairness by disrupting meiotic drive \citep{Rice2013}.

@@

In the standard single-locus, biallelic model of female meiotic drive,
the driving allele is transmitted to the egg in heterozygotes with
probability  $d > 1/2$, regardless of sperm genotype (Model 1) \cite[e.g. ][]{Ubeda2004}. The timing of fertilization relative to female meiosis places another constraint on $d$, for example, if fertilization (and therefore, sperm dependent drive) takes place at MII (as in mammals),
	female drive requires an uneven number of crossovers between the centromere and the drive locus, 
	so $d$ is bounded to be $<0.83$ \citep[see ][ for
        discussion]{Buckler1999}.  To depict a case
of a self-promoting meiotic driver,  we modify this standard model such 
	that the driver is only effective when fertilized by a sperm carrying that allele (see Figure \ref{Eggsperm_2_allele_cartoon} and Model 2 in the Supplementary Worksheet). 
We then identify the conditions allowing for the spread of this self-promoting driver, 
	and evaluate whether a driver of this form could generate a sustained conflict favoring the evolution of suppressors. 
We concluded with an analysis of a related model (Model 3) - in which
drivers influence their transmission in females via paternal genotype,
rather than sperm haplotype.

@@

When a self-promoting driver does spread, 
	it spends much time at low frequency, 
	because the paucity of complimentary sperm compromises its ability to drive. 
However, once relatively common, it  rapidly achieves fixation due to its
	positive frequency dependent behavior (Inset in Figure \ref{Invasion_space}).  
%This lack of a balanced polymorphism %(Figure \ref{Invasion_space}) 
%	precludes the evolution of an
%	allele that suppresses this form of meiotic drive in females.
The positive frequency dependence of a self-promoting driver can also
	induce bistability in its spread -- some values of $s$ 
	allow the fixation of this driver when common, but 
	preclude its invasion when rare (Equation \ref{ineqA}). 
In this case, the driver will be fixed if it reaches a frequency greater than some threshold 
	(approximated in Equation \ref{bistab_homozy_approx} and  presented exactly in 
	Figure \ref{Bistab_homozyg_cost_fig}) and lost otherwise. 
For most parameters, this threshold is likely too high to be reached by drift, 
	and therefore  the fate of self-promoting drivers is determined
	by the more restrictive invasion criteria rather than the fixation criteria.

@@

%OLD YANIV WORDS
% Compared to the invasion criteria, the parameter space
% allowing the fixation of the allele if it is above a cutoff frequency is much broader -- 
% 	a common, recessive, self-promoting driver fixes if
%         $s<(2d-1)/2$ approximately. 
% Therefore, when $(2 d - 1)/(4 d)<s<(2d-1)/(2)$, 
% 	a recessive, self-promoting driver will deterministically fix if drift, mutation, 
% 	or migration pressure bring its frequency above $(1-2d+4ds)/(2s(2d-1))$, 
% 	but it will be lost otherwise.
Inclusion of a heterozygous fitness cost (i.e. $w_{AB}=1-s_h$)
	further constrains the evolution of a self-promoting driver. 
In fact, with any heterozygous fitness cost, a rare self-promoting
	driver is always selected against. 
However, this case also displays bistability -- 
	when $s$ is sufficiently small (Equation \ref{sForHetFix}) this allele fixes deterministically if its 
	frequency exceeds some threshold  (Equation \ref{thresh2}, exact results in 
	Figure \ref{bistable_additive}).
%	$f_B^*$
%	because it pays the  heterozygous fitness cost but drives
 %      ineffectively (see Figure S\ref{bistable_additive})
%While a standard female driver invades from low frequency when the transmission advantage outweighs the fitness cost (XXX),
%	a rare self-promoter pays a fitness cost, but drives only weakly because complementary sperm are uncommon. 
%This frequency-independent fitness cost, and positive frequency dependent drive generates a bistable system. 
%Below a cutoff frequency the self-promoter driver deterministically decreases in frequency 
%	because it pays the  heterozygous fitness cost but drives
 %      ineffectively (see Figure S\ref{bistable_additive}). 
%Above this frequency, the allele increases deterministically because the commonness of complementary sperm 
%	make drive effective enough to overcome the associated fitness cost.
This bistability prevents self-promoting drivers from invading 	
	reasonably sized populations, and assures that if they do invade, they will rapidly fix.
Our model therefore predicts that self-promoting drivers will not be
	observed as stable polymorphisms in natural populations. 
This lack of a balanced polymorphism %(Figure \ref{Invasion_space}) 
	precludes the evolution of an
	allele that suppresses this form of meiotic drive in females.

Although the allelic identity of sperm could plausibly influence the outcome of female meiosis, 
	limited gene expression in sperm \citep[e.g.][]{Joseph2004}
	suggests a model where sperm influence female meiosis via expression of the fertilizing male's
	diploid genotype (perhaps due to proteins and RNAs packaged into the sperm), rather than sperm haplotype.
This paternal-genotype dependent model (Model 3) requires one additional parameter, as we exchange $d$ in the sperm dependent case for $d_{het}$ and $d_{hom}$ which describe the transmission of the drive allele in a heterozygous female mating with males heterozygous and homozygous for the self-promoting drive allele, respectively.  
Here, a rare driver invades when $s$ is less than $(d_{het}-1/2)/d_{het}$, and usually fixes when it invades.
	% fixes when $s$ is less than $d_{hom} - 1/2$.
However, when the distorting effect of genotype displays strong dominance in its
	effect on female meiosis ($d_{het}$ is close to $d_{hom}$), 
	there is a a narrow sliver of parameter space sustains a polymorphism
	when the cost of the drive is recessive
	(see Figure \ref{Effect_of_dominance}, and Equation \ref{polymale}).  
%Presumably this zone of polymorphism comes about because positive frequency 
%	dependence diminishes with the dominance of the male effect driver. 
%As an analytical example, consider the case of male-genotype dependent deleterious recessive female driver (assuming, as above, $w_{BB}=1-s$, and $w_{AA}=w_{AB}=1$). 
%Here, a rare driver invades when $s$ is less than $(d_{het}-1/2)/d_{het}$, and fixes when $s$ is less than $d_{hom} - 1/2$.
%Intermediate values of $s$, which represent a small proportion of parameter space can maintain a polymorphism. 
While mathematically interesting, it does not seem particularly realistic to think that the
	effect of the drive allele would be dominant in its action through the
	male genotype, while the cost would be recessive. 
Therefore, although Model 3 can sustain a polymorphism, 
	the lack of biological reality underlying the small portion of parameter values 
	required for this polymorphism make us doubt it general applicability. 
%Thus we regard this case as interesting but not very general.

@@

Models 2 and 3, above, explored the dynamics of an allele that drove in females when signaled by a complementary signal in sperm.   
We complement this single-locus approach %of an allele with pleiotropic effects in both sexes, 
	with alternative models of two loci - one a female driver, 
	and the other, a sperm allele which modifies the effect of drive upon fertilization. 
In this model, a female meiotic driver with no sperm-dependency 
	initially reaches drive-viability equilibrium (with two alleles
	$A$ and $B$ are the ancestral non-driver and driver alleles). 
Subsequently, a sperm-acting modifier of female meiotic drive arises at another lous.

We first assume that the modifier is tightly
        linked to the drive locus (effectively creating a third
        allele/haplotype at this locus) and arises on the drive-background. 
%We complement this single-locus approach %of an allele with pleiotropic effects in both sexes, 
%	with alternative models of two linked loci - one a female driver, 
%	and the other, a sperm allele which modifies the effect of drive upon fertilization. 
%In this model, a female meiotic driver with no sperm-dependency 
%	initially reaches drive-viability equilibrium (with two alleles
%	$A$ and $B$ are the ancestral non-driver and driver alleles). 
%Subsequently, a sperm-acting modifier of female meiotic drive arises tightly
 %      linked to this balanced locus (effectively creating a third
 %       allele/haplotype at this locus). 
Tight linkage offers the best
        chance for a collaboration to evolve between a driver and
       an enhancer of the drive, as recombination breaks up drive haplotypes \citep{Thomson1974,Charlesworth1978,Haig1991}. 
Additionally, tight linkage between female driver and sperm modifier is consistent with the nature of well characterized drive systems which are often maintained as polymorphic inversions with numerous linked modifiers \cite{Burt2006}. 
\yb{We conclude by analyzing models with alternative linkage relationship between driver and drive modifier - 
	in Model 5 the modifier arises tightly linked to the non-driving allele, 
	and in Model 6 it is unlinked to the driver.}

@@

%%%sperm-acting facilitator
When the modifier of drive is tightly linked to the driver and enhances drive, 
	we label  this non-recombining drive/modifier haplotype as the $B^+$ allele.  
%We first consider a sperm-acting modifier of
%	female meiotic drive tightly linked to the $B$ background (Model 4).
%We treat this non-recombining drive/modifier haplotype as a third allele, and we label this allele as $B^+$ when it enhances drive. 
%(i.e. the non-recombining haplotype of a
 %       driver allele and sperm-acting drive modifier)
%The $B^+$ allele 
%	the $B$ and  $B^{+}$ drive in $AB$ and $AB^{+}$ heterozygotes (see Figure \ref{Eggsperm_3_allele_cartoon})
%		generating a third `$B^{+}$' allele (i.e. the non-recombining haplotype of a
   %     driver allele and sperm-acting drive modifier). 
The $B^+$ allele acts in sperm to increase the effectiveness of drive for both
	the $B$ and  $B^{+}$ alleles in $AB$ and $AB^{+}$ heterozygotes (see Figure \ref{Eggsperm_3_allele_cartoon}, and Model 4 in the Supplementary Worksheet). 
%	for a simple schematic of this drive model.  
Naively, $B^{+}$ may spread by capitalizing on the additional drive it causes; however,  
	this is not the case for a few simple reasons. 
First, %the sperm-acting drive facilitator (
	the novel $B^{+}$ haplotype
	%) 
	arises when the ancestral driver 
	%($B$) 
	is at drive-selection balance, 
	and therefore immediately suffers a homozygous fitness cost.  
Worse yet, a novel $B^{+}$ haplotype most often helps 
	the $B$  allele drive ($B^+$ sperm meeting $AB$ eggs), because $B$ is initially more common than $B^{+}$. 
%As $B^{+}$ facilitates $B$ these interactions frequently form 
%	$BB^{+}$ heterozygotes that suffer the same fitness costs as $BB$. 
Therefore, sperm-acting drive facilitator alleles experience a profound disadvantage 
	in this scenario, even more so than under the previous two allele model. 
We have found no parameter range of this
	three allele system that allows the sperm-acting drive facilitator $B^{+}$ to
	invade the population (Appendix Model 4, eqn. \eqref{coupling}, and Mathematical Supplement).

%%%sperm-acting drive suppressors
While  sperm enhancement of a female drive cannot displace a polymorphic female driver, sperm based drive suppressors can. 
%	that is sperm-acting alleles that act to restore  fairness of female meiosis, can. %If these sperm-acting drive suppressors arise on
If a sperm-acting allele that restores fairness to female meiosis arises on
	the drive background (creating a third allele $B^{-}$, Model 4), it displaces the ancestral driver (Equation \ref{coupling}), 
	and often returns to a lower equilibrium frequency than the the $B$ allele, further decreasing the extent of drive in the population.  
If this sperm-acting drive suppressor arises on 
	the non-driving $A$ background (creating a third allele $A^{-}$, Model 5), 
	or is unlinked to the drive locus (Model 6), it readily invades a population segregating
	for the drive system (Figure \ref{Eggsperm_3_allele_cartoon} and eqns \ref{A-} and \ref{unlinked}).  
This allele lowers the frequency of the original driver (perhaps to zero),
	and spreads to fixation if it does not carry strong fitness costs
	(Figure \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}A). 
This result is consistent with previous work showing that drive suppressors unlinked to, or in repulsion phase with drivers usually invade polymorphic drive systems \citep[e.g. ][]{Brandvain2012}.  
Therefore, all two-locus models of sperm influence on female drive suggest that
	sperm will evolve to oppose female meiotic drive.
